A Large-Scale Study of the Use of Eval in R

### 2020-08-23 inst/paper/main.tex
related

\title{A Large-Scale Study of the Use of Eval in R}
\author{\vspace{-.8cm}\IEEEauthorblockN{
    \it\Large The Eval that Data Scientists Do}%
  %\IEEEauthorblockA{ dept} \\ \and
}  
\maketitle

@@

\section{Related Work}

\cite{ecoop11}

@@

\section{Shades of Eval}

- Talk about environments
- How is it different from JS (takes language, env in R but string in JS).

@@

\begin{lstlisting}
eval <- function (expr, envir = parent.frame(), enclos = if (is.list(envir) || is.pairlist(envir)) parent.frame() else baseenv())  
	.Internal(eval(expr, envir, enclos))
\end{lstlisting}

>>>>

\title{A Large-Scale Study of the Use of Eval in R}
\author{\vspace{-.8cm}\IEEEauthorblockN{~}} %\IEEEauthorblockA{ dept} \\ \and
\maketitle

@@

\section{Background and Related Work}

The origins of \eval go back to the first implementation of the Lisp
programming language~\cite{lisp}. Over the years, \eval has been included in
many dynamic languages, with some variability in expressive power and
nomenclature. In all of its incarnation \eval allow developpers to
dynamically extend the code of their program at run-time.  Originally, \eval
was limited to interpreted languages, but with the advent of just-in-time
compilation this restriction was gradually lifted.

Some languages have chosen to restrict \eval. The essential difference
between languages relates to scoping of variables that can be accessed from
code executed by \eval.  Java and Julia are among the more restrictive
languages. In Java, \eval must be synthesized as a combination dynamic
loading and reflection.\footnote{While Java does not have \eval built in,
  one can take the input to \eval, wrap it in a static method of an
  anonymous class, generate bytecode for that class, invoke the Java class
  loader to dynamically install it, and then use reflection to call the new
  method.} Julia provides \eval more directly but limits its scope to top
level variables and methods. JavaScript support both a, so-called, global
\eval, and a local \eval. Where the latter has acces to local variables of
the function being executed (as well as variables of lexically enclosing
scopes). Finally languages such as R allow \eval to manipulate variables
defined in the caller environment of the function in which \eval is invoked.

The difference between these design choices has an impact on the ability of
compilers to optimize, and of analysis tools to reason about, code. The
impact of a top level \eval is that any global definition may be affected
but the current function can continue to execute unchanged. A local \eval
may change the value of local variables, their types, or even their
presence. This is a much more invasive change for reasoning about code and
may invalidate common optimizations such as constant folding or copy
propagation. The designers of Julia were aware of this difference and chose
to restrict \eval to preserve their ability to compile
code~\cite{oopsla18a}. They even added a versioning mechanism to function
definitions to ensure that new code added during an \eval would not
invalidate optimizations such as inlining.  R's ability to affect any one of
the callers of a function is even more invasive as the impact of \eval is
non-local. Such unfettered power is difficult to deal with.

@@

@@

\begin{lstlisting}
  eval <- function(expr, envir=parent.frame(),
                   enclos=if (is.list(envir)||is.pairlist(envir)) parent.frame() else baseenv())  
	.Internal(eval(expr, envir, enclos))
\end{lstlisting}
